Exploring n_tags

### 2017-08-05 tag_exploration.Rmd
set up a CR model similar to one described in literature review, compared results

top50 <- tag_freq[1:50,]
ggplot(top50, aes(x = fct_reorder(tag, -percent), y = percent)) + 
  geom_col() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  scale_y_continuous(labels = scales::percent) + 
  ggtitle("Distribution of the top 50 tags and percentage of times they occur in the data")
```

@@

@@

>>>>

top50 <- tag_freq[1:50,]
ggplot(top50, aes(x = fct_reorder(tag, -percent), y = percent)) + 
  geom_point() + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) + 
  scale_y_continuous(labels = scales::percent) + 
  ggtitle("Distribution of the top 50 tags and percentage of times they occur in the data")
```

@@

ggplot(x, aes(x = score1)) + 
  geom_histogram()
ggplot(x, aes(x = score2)) + geom_histogram()
ggplot(x, aes(x = score3)) + geom_histogram()
ggplot(x, aes(x = score4)) + geom_histogram()

@@

##### Counting of popular tags a question has 
```{r}
threshold <- 0.005

num_pop <- function(var, threshold) {
  num_pop <- rep(0, nrow(x))
  num_pop[x[[var]] >= threshold] <- 1
  return(num_pop)
}

numpop1 <- num_pop("score1", threshold)
numpop2 <- num_pop("score2", threshold)
numpop3 <- num_pop("score3", threshold)
numpop4 <- num_pop("score4", threshold)

x$num_freq_tags <- numpop1 + numpop2 + numpop3 + numpop4

```
